Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-04-11 article/article.Rmd
+ article fixes + projected bioclim pca layer
Former-commit-id: eda1d553c0e5173c94f928353a61c1d1f9fbeb70

## Introduction
<!--  main text -->
The act of setting aside areas for preservation spearheads modern conservation efforts [@r440]. Protected area networks buffer species from anthropogenic impacts and provide places for populations of species to persist. Intra-specific genetic variation underpins species persistence, and there has been increasing interest in understanding how to design protected area networks in a way that maximizes this variation [@r67; @r3; @r61]. Broadly speaking, genetic variation can be classified as either adaptive or neutral [reviewed in @r48]. Adaptive genetic variation is associated with loci that affect fitness. By preserving existing patterns of adaptive variation, protected areas can ensure that populations with particularly beneficial adaptations are not lost [@r3]. In contrast, neutral genetic variation is associated with loci that do not affect fitness. Neutral variation often reflects the evolutionary history of different populations. By preserving existing patterns of neutral variation, protected areas can secure different genetic lineages and avoid the adverse effects of low genetic diversity [eg. inbreeding depression; @r67]. However, genetic data requires considerable investment to obtain and analyze. As a consequence, conservation planners do not typically use genetic data to inform prioritizations [@r61]. Thus prioritizations may fail to capture species' intra-specific genetic variation, and ultimately fail to deliver long-term conservation outcomes.

>>>>

## Introduction
<!--  main text -->
The act of setting aside areas for preservation is one of the hallmarks of modern conservation [@r440]. Protected area networks buffer species from anthropogenic impacts and provide places for populations of species to persist. Intra-specific genetic variation is an important component of species persistence, and there has been increasing interest in understanding how to design protected area networks that preserve this variation [@r67; @r3; @r61]. Broadly speaking, genetic variation can be classified as either adaptive or neutral [reviewed in @r48]. Adaptive genetic variation is associated with loci that affect fitness. By preserving existing patterns of adaptive variation, protected areas can ensure that populations with particularly beneficial adaptations are not lost [@r3]. In contrast, neutral genetic variation is associated with loci that do not affect fitness. Neutral variation often reflects the evolutionary history of different populations. By preserving existing patterns of neutral variation, protected areas can secure different genetic lineages and avoid the adverse effects of low genetic diversity [eg. inbreeding depression; @r67]. However, genetic data requires considerable investment to obtain and analyze. As a consequence, conservation planners do not typically use genetic data to inform prioritizations [@r61]. Thus prioritizations may fail to capture species' intra-specific genetic variation, and ultimately fail to deliver long-term conservation outcomes.
